A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-02-17 writeup/paper.tex
Minor tweaks to abstract, author info

\author{Ellie Pavlick  \\
  \small {\tt elliepavlick@gmail.com} \normalsize \\
  \And
  Dmitry Kachaev  \\
 \small  {\tt dmitry.kachaev@gmail.com } \normalsize \\
  \And
  Chris Callison-Burch \\
 \small  {\tt ccb@seas.upenn.edu} \normalsize \\
  }

@@

\begin{abstract}
We present a large scale study of the languages spoken by bilingual workers on Mechanical Turk (MTurk).  
We establish a  methodology for determining the language skills of anonymous crowd workers that is more robust than simple surveying.  We validate workers' self-reported language skills claims by measuring their ability to correctly translate words, and by geolocating workers to see if they come from a country where the language is spoken. Rather than posting a one-off survey, we posted large-scale, paid tasks consisting of 1,000 assignment to translate a total of 10,000 words in each of 100 languages.  Our study ran for weeks, and was highly visible on the MTurk crowdsourcing platform, increasing the chances that bilinguals workers would have seen.  Our study resulted in the creation of bilingual dictionaries for a wide variety of languages, and acted as census of the bilingual speakers on MTurk.  We use this to recommend languages with the largest speaker populations that are good candidates for other researchers who want to  develop crowdsourced, multilingual technologies.

>>>>

\author{Ellie Pavlick \ \ \ \ \ \ \ \ \ \ Dmitry Kachaev \ \ \ \ \ \ \ \ \ \  Chris Callison-Burch \\
Computer and Information Science Department, University of Pennsylvania \\
Human Language Technology Center of Excellence, Johns Hopkins University \\
  }

@@

\begin{abstract}
We present a large scale study of the languages spoken by bilingual workers on Mechanical Turk (MTurk).  
We establish a  methodology for determining the language skills of anonymous crowd workers that is more robust than simple surveying.  We validate workers' self-reported language skill claims by measuring their ability to correctly translate words, and by geolocating workers to see if they reside in countries where the languages are likely to be spoken. Rather than posting a one-off survey, we posted paid tasks consisting of 1,000 assignments to translate a total of 10,000 words in each of 100 languages.  Our study ran for weeks, and was highly visible on the MTurk crowdsourcing platform, increasing the chances that bilinguals workers would have seen it.  Our study was useful both to create bilingual dictionaries and to act as census of the bilingual speakers on MTurk.  We use this data to recommend languages with the largest speaker populations as good candidates for other researchers who want to  develop crowdsourced, multilingual technologies.
